Light Transport Techniques for Tensor Field Visualization

### 2019-07-25 beamer2thesis/dummy.tex
update

\documentclass[aspectratio=169]{beamer}
\usetheme[language=ngerman,
titlepagelogo=logopolito,
bullet=circle,
pageofpages=of,
titleline=true,
color=blue
]{TorinoTh}

%\usepackage[ngerman]{babel}
%\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{ulem}
\usepackage{makecell}
\usepackage{upgreek}
\usepackage{movie15}
%\usepackage{isodate}

\addto{\captionsngerman}{%
  \renewcommand*{\contentsname}{Contents}
  \renewcommand*{\listfigurename}{Figures}
  \renewcommand*{\listtablename}{Tables}
  \renewcommand*{\figurename}{Fig.}	
  \renewcommand*{\tablename}{Tab.}
}
\newcommand*\mean[1]{\bar{#1}}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\newcommand\widebar[1]{\mathop{\overline{#1}}}

@@

%\color{unirot}{sebibek@gmail.com}
%\newsubfloat{figure}
\newcommand{\source}[1]{\vspace{-3pt} \caption*{ Source: {#1}} }
\setlength{\belowcaptionskip}{-10pt}
\setlength{\intextsep}{-30pt}

@@

%\frame[plain]{\titlepage}

\frame{
\frametitle{{Light Transport Gradient - Heart dataset}}
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
   \centering
  \includegraphics[width=0.7\textwidth]{heartDwnsmpl.png}
	a)
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
   \centering
    \includegraphics[width=0.7\textwidth]{heartDwnsmpl-TFL.PNG}
	b)
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
   \centering
    \includegraphics[width=0.7\textwidth]{heart_ftle_org.PNG}
	c)
    \label{b)}
  \end{minipage}
\caption{Heart test field: a) glyphs, b) TFLs, c) FTLE: H.'s approach}
\label{heart-ftle-comp}
\end{figure}

\begin{itemize}
	\item No noise present in the Heart dataset $\Rightarrow$ TFLs reveal correlated trajectories
	\item FTLE response on structure obtained in the style of Hlawatsch et al.
\end{itemize}
} % END OF FRAME

\frame{
\frametitle{{Heart dataset - Evaluation}}
\begin{figure}[!t]
\centering
  \begin{minipage}{0.3\textwidth}
  \centering
  \includegraphics[height=0.9\textwidth]{heartDwnsmpl.PNG}
	a)
    \label{a)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[width=0.9\textwidth]{heart_ftle_org.PNG}
	b)
    \label{b)}
  \end{minipage}
  \begin{minipage}{0.3\textwidth}
  \centering
    \includegraphics[width=0.9\textwidth]{heart_slice20_rescale.PNG}
	c)
    \label{b)}
  \end{minipage}
  \caption{Heart test field: a) Glyphs, b) LTG local, c) LTG local (rescale)}
\label{heart-ftle}
\end{figure}
\begin{itemize}
	\item light ridges enhanced by rescaling for the down-left direction (red lines in c))
	\item regions exhibit most drastic changes in anisotropy and/or divergence for TFLs
	\item edge artifacts: edges effect high gradients for the flow map
\end{itemize}
} % END OF FRAME

%Volume non-directionally dependent

>>>>

\documentclass[aspectratio=169,urlcolor=black]{beamer}
\usetheme[language=ngerman,
titlepagelogo=logopolito,
bullet=circle,
pageofpages=of,
color=blue,
titleline=true
]{TorinoTh}

%\usepackage[ngerman]{babel}
%\usepackage[utf8]{inputenc}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{ulem}
\usepackage{makecell}
\usepackage{upgreek}
\usepackage{movie15}
%\usepackage{xcolor}
%\usepackage{isodate}
\hypersetup{colorlinks,linkcolor=black,urlcolor=black}
\addto{\captionsngerman}{%
  \renewcommand*{\contentsname}{Contents}
  \renewcommand*{\listfigurename}{Figures}
  \renewcommand*{\listtablename}{Tables}
  \renewcommand*{\figurename}{Fig.}	
  \renewcommand*{\tablename}{Tab.}
}
\newcommand*\mean[1]{\bar{#1}}
\newcommand{\tabitem}{~~\llap{\textbullet}~~}
\newcommand\widebar[1]{\mathop{\overline{#1}}}

@@

%\color{unirot}{sebibek@gmail.com}
%\newsubfloat{figure}
\newcommand{\source}[1]{\hspace{-3pt} {\tiny \raisebox{-0.75in}{\rotatebox[origin=t]{90}{Source: \color{black}{#1}}}}}
\setlength{\belowcaptionskip}{-10pt}
%\setlength{\intextsep}{-30pt}

@@

%\frame[plain]{\titlepage}
\frame{
\frametitle{{Finite-Time Lyapunov exponents}}

\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Definition}}
Local: 
$
	\sigma = \frac{1}{\lvert T\rvert}\ln \frac{\Delta}{\delta}
$\\
Global: 
$
	\sigma(\mathbf{x})=\frac{1}{\lvert T\rvert}\ln \|\nabla\mathbf{\upvarphi(x)}\|_2
$\\
{\scriptsize whereas $\| A\| _2 = \sqrt{\lambda_{max}(A^TA)}$ is the spectral norm of matrix $A$}
\end{block}
\end{small}
\begin{itemize}
	\item measure for separation abilities of LTV (time-variant) systems concerning massless tracer particles
	\item Lagrangian view in vector fields: placing two close-by particles into and moving with the flow
\end{itemize}

\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\begin{minipage}{0.85\textwidth}
\centering
\includegraphics[height=0.6\textwidth]{gyre_rot.pdf} a)
\includegraphics[height=0.6\textwidth]{ftle_sep.pdf} b)
\caption{a) Vector field, b) diverging pathlines}
\end{minipage}
\begin{minipage}{0.1\textwidth}
\source{b) Skript Prof. Sadlo, SciVis SS2017}
\end{minipage}

\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

\frame{
\frametitle{{Finite-Time Lyapunov exponents}}

\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{block}{\centering \textbf{Definition}}
Local: 
$
	\sigma = \frac{1}{\lvert T\rvert}\ln \frac{\Delta}{\delta}
$\\
Global: 
$
	\sigma(\mathbf{x})=\frac{1}{\lvert T\rvert}\ln \|\nabla\mathbf{\upvarphi(x)}\|_2
$\\
{\scriptsize whereas $\| A\| _2 = \sqrt{\lambda_{max}(A^TA)}$ is the spectral norm of matrix $A$}
\end{block}
\end{small}
\begin{itemize}
	\item measure for separation abilities of LTV (time-variant) systems concerning massless tracer particles
	\item Lagrangian view in vector fields: placing two close-by particles into and moving with the flow
\end{itemize}

\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\centering
\includegraphics[height=0.35\textwidth]{gyre.pdf}~a)
\includegraphics[height=0.35\textwidth]{ftle.png}~b)
\caption{a) Vector field, b) FTLE field}

\end{figure}

\end{column}
\end{columns}
} % END OF FRAME

%glyphs are used to represent the eigensystem, i.e., the anisotropy characteristics and/or tensor magnitude
%Volume non-directionally dependent
